Delta Smelt Enclosure Study 2019 Hybrid Paper Diet Analysis

### 2022-11-18 smelt_2019_allseasons/Zoop 2019.Rmd
zoop plot edits

ggplot() +
  geom_bar(position = "fill", stat = "identity", data=caught.sea, aes (x=Location, y=sum.count, fill=Taxa), colour="black", width = .5) +
  facet_wrap(~Season, ncol = 1) +
  theme_bw() + 
  viridis::scale_fill_viridis(discrete = TRUE, option = "plasma") +
  labs(x = "Location") +
  labs(y = "Relative Abundance")+
  theme(legend.position="right")+
      theme(axis.text = element_text(size = 12),
      axis.title = element_text(size = 12),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 10))

@@

ggplot() +
  geom_bar(position = "fill", stat = "identity", data=caught.sea2, aes (x=Location, y=sum.count, fill=Taxa), colour="black", width = .5) +
  facet_wrap(~Season, ncol = 1) +
  theme_bw() + 
  viridis::scale_fill_viridis(discrete = TRUE, option = "plasma") +
  labs(x = "Location") +
  labs(y = "Relative Abundance")+
  theme(legend.position="right")+
      theme(axis.text = element_text(size = 12),
      axis.title = element_text(size = 12),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 10))

>>>>

ggplot() +
  geom_bar(position = "fill", stat = "identity", data=caught.sea, aes (x=Location, y=sum.count, fill=Taxa), colour="black", width = .75) +
  facet_wrap(~Season, ncol = 1) +
  theme_bw() + 
  viridis::scale_fill_viridis(discrete = TRUE, option = "plasma") +
  labs(x = "Location") +
  labs(y = "Relative Abundance")+
  theme(legend.position="right")+
      theme(axis.text = element_text(size = 12),
      axis.title = element_text(size = 12),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 10))

@@

ggplot() +
  geom_bar(position = "fill", stat = "identity", data=caught.sea2, aes (x=Location, y=sum.count, fill=Taxa), colour="black", width = .75) +
  facet_wrap(~Season, ncol = 1) +
  theme_bw() + 
  viridis::scale_fill_viridis(discrete = TRUE, option = "plasma") +
  labs(x = "Location") +
  labs(y = "Relative Abundance")+
  theme(legend.position="right")+
      theme(axis.text = element_text(size = 12),
      axis.title = element_text(size = 12),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 10))
